\subsection{Why do the cross-project feature fusion layers work? }

\subsection{Why does TRANP-CNN improve the bug localization performance?}

\subsection{Threats to Validity}

\dl{Ferdian, please help to fill in the blanks.}

There are three kinds of threat that may impact the validity of this study: threats to internal validity, threats to external validity, and threats to construct validity. We acknowledge these threats below.

Threats to internal validity relate to author bias and errors in our code and experiments. We have checked our code for bugs and fixed any that we can identify. There may still be errors that we do not notice though. The dataset that we obtain are taken from prior papers~\cite{zhou2012should,KochharTL14} and have been used to evaluate other bug localization techniques, e.g.,~\cite{zhou2012should,SahaLKP14,huo2016learning}. The data are bug reports taken from bug tracking systems from real projects (i.e., ....) and thus are realistic. Thus, we believe there are limited threats to the internal validity of the study. 

Threats to external validity relate to the generalizability of the study. We have analyzed data that includes ... bug reports taken from ... projects. Admittedly, the projects that we analyze may not represent all the projects out there. Still, our threats to external validity are less than existing bug localization work since the amount of data that we investigate is larger than prior work. For example, Zhou et al. only use ... bug reports from ... projects~\cite{zhou2012should}, Saha et al. only use ... bug reports from ... reports~\cite{SahaLKP14}, and Huo et al. only use ... bug reports from ... projects~\cite{huo2016learning}. In a future work, we plan to reduce the threats to external validity further by investigating more bug reports from additional projects.

Threats to construct validity relate to the suitability of our evaluation metrics. We have used ... as evaluation metrics. These metrics were also used by prior bug localization studies, e.g.,  ~\cite{zhou2012should,SahaLKP14,huo2016learning}. Thus, we believe there are limited threats to construct validity. 